### 2014-03-12 LaTeX/RhodiumConcl.tex
Model updates, slight outline updates

If NATO had not intervened, the expected duration of the conflict would have been much shorter. But the rebels would have lost, so there is a trade-off.

>>>>

\begin{itemize}
	\item Note that sub-state conflict location may have implications for contagion.  Are regional economic consequences of civil war not a function of civil war existence but proximity of the conflict to cities or resources in neighboring states?
\end{itemize}
